Representation Learning for Generalized Planning - SAT Encodings

### 2021-04-19 doc/paper/paper.tex
minor changes in doc

Let the transitions be defined as $s \rightarrow a \rightarrow s' \rightarrow s"$, where the agent executes a in the state s and goes to some $s'$, and then the nature or the adversary (doing anything) turns $s'$ into $s''$. Therefore the transitions $(s, s')$ is deterministic and the transition $(s, s'')$ is non-deternimistic.

\begin{itemize}
 \item $Good(s, a)$ for $s$ alive, $s''$ solvable. Where $V(s'') < V(s)$.

 \item $Good(s, s')$ for $s$ alive, $s'$ solvable and $(s, s') \not\in \badtx$.

@@

\smallpar{C1}
The policy has to be complete with respect to all alive states:
\begin{align}
\bigvee_{s' \text{ s.t. } (s, s') \in T \setminus \badtx} Good(s, s'),&\;\; \text{for $s$ alive.}
\end{align}

\smallpar{C2} $V$ is always descending along Good transitions:
\begin{align}
 Good(s, s') \land V(s', d) \rightarrow \bigvee_{d < k \leq D} V(s, k),&\;\; \text{for $s, s'$ alive, $(s, s') \not\in \badtx$, $d \in [1, D)$.} \\
 V(s', D) \rightarrow \neg Good(s, s'),&\;\; \text{for $s, s'$ alive, $(s, s') \not\in \badtx$.} \tag{\theequation${}^\prime$}
\end{align}

\smallpar{C3 (Optional)} All descending transitions must be considered Good:
\begin{align}
 V(s, d) \land V(s', d') \rightarrow Good(s, s'),&\;\; \text{for $s, s'$ alive, $(s, s') \not\in \badtx$, $1 \leq d' < d \leq D$,} \\
 Good(s, s'),&\;\; \text{for $s$ alive, $s'$ goal.} \tag{\theequation${}^\prime$}
\end{align}

@@

\smallpar{C5-6}
Good transitions can be distinguished from bad transitions.
Let $(s, s')$ and $(t, t')$ be \emph{representative} transitions
of two different equivalence classes such that $(s, s') \not\in \badtx$
(which implies that $s'$ is solvable). Then,

\begin{align}
 Good(s, s') \rightarrow Good(t, t') \lor
 Dist(s, s', t, t'),&\;\; \text{for $s, t$ alive, $(t, t') \not\in \badtx$.} \\
 Good(s, s') \rightarrow
 Dist(s, s', t, t'),&\;\; \text{for $s, t$ alive, $(t, t') \in \badtx$.}
\end{align}

>>>>

In any non deterministic domain the agent can go a pull of states $S'$ by executing an action $a$ in the state $s$, and then the nature or the adversary (doing anything) turns $s'$ into $s''$. Then all the transitions holds in the form $s \rightarrow a \rightarrow s'$, where $s' \epsilon~S'$.

%We define the adversarial setting as transitions defined by $s \rightarrow a \rightarrow s' \rightarrow s"$, where the agent executes a in the state s and goes to some $s'$, and then the nature or the adversary (doing anything) turns $s'$ into $s''$. Therefore the transitions $(s, s')$ is deterministic and the transition $(s, s'')$ is non-deternimistic. If there is no possible $s''$ outgoing from $s'$ we just set $s'' = s'$.

%If we are in a completely non-deterministic setting we can make it hold in the previous definition just by setting $s' = s''$.

%We can face two different situations. One in which the actions space is defined and never change from one instance to another. In the other situation we have no defined action space $A$. When we are facing a non defined $A$, we just define the actions as efects to be discovered implicitly in the transitions $s \rightarrow s'$.

\begin{itemize}
 \item $Good(s, a)$ for $s$ alive, $s'$ solvable for all possible $s'$ result of executing a in $s$.

 \item $Bad(s)$ for $s$ alive.

 %\item $Good(s, s')$ for $s$ alive, $s'$ solvable and $(s, s') \not\in \badtx$.

@@

\smallpar{C1}
The policy has to be complete with respect to all possible actions applicable in s:
\begin{align}
\bigvee_{a \text{ s.t. } (s, a, S') \in T} Good(s, a),&\;\; \text{for $s$ alive.}
\end{align}

\smallpar{C2} $V$ is always descending along Good actions:
\begin{align}
 Good(s, a) \land V(s', d) \rightarrow \bigvee_{d < k \leq D} V(s, k),&\;\; \text{for $s, a$ alive, $(s, a) \not\in \badtx$, $d \in [1, D)$.} \\
 V(s', D) \rightarrow \neg Good(s, a),&\;\; \text{for $s, a$ alive, $(s, a) \not\in \badtx$.} \tag{\theequation${}^\prime$}
\end{align}

\smallpar{C3} All descending transitions must be considered Good:
\begin{align}
 V(s, d) \land V(s', d') \rightarrow Good(s, a),&\;\; \text{for $s, s'$ alive, $(s, a, s') \not\in \badtx$, $1 \leq d' < d \leq D$,} \\
 Good(s, a),&\;\; \text{for $s$ alive, $s'$ goal.} \tag{\theequation${}^\prime$}
\end{align}

@@

\smallpar{C5-6}
Good pairs (s, a) can be distinguished from bad pairs (s, a).
Let $(s, a)$ and $(s, a')$
of two different equivalence classes such that $(s, a, S') \not\in \badtx$
(which implies that any $s' \in S'$ is solvable). Then,

%\smallpar{C5-6}
%Good transitions can be distinguished from bad transitions.
%Let $(s, s')$ and $(t, t')$ be \emph{representative} transitions
%of two different equivalence classes such that $(s, s') \not\in \badtx$
%(which implies that $s'$ is solvable). Then,
%\begin{align}
% Good(s, s') \rightarrow Good(t, t') \lor
% Dist(s, s', t, t'),&\;\; \text{for $s, t$ alive, $(t, t') \not\in \badtx$.} \\
% Good(s, s') \rightarrow
% Dist(s, s', t, t'),&\;\; \text{for $s, t$ alive, $(t, t') \in \badtx$.}
%\end{align}
